\texttt{escheR}: Unified multi-dimensional visualizations with Gestalt principles

### 2023-05-09 Manuscript/manuscript.tex

\subsection*{Availability and implementation}
The open source R package \texttt{escheR} is freely available on GitHub and is being submitted to Bioconductor (\href{https://github.com/boyiguo1/escheR}{https://github.com/boyiguo1/escheR}).
% and Zenodo (\fixme{add link}).

@@

Here, we provide an open-source package called \texttt{escheR} (named after the graphic artist M.C. Escher) in the R programming language \cite{R}, leading to a simplified interface to navigate the implementation of the multi-dimensional visualization in 2D space. By adapting \texttt{ggplot2} standard, \texttt{escheR} can be seamlessly integrated into many popular spatial resolved toolboxes, such as \texttt{SpatialLIBD}\cite{pardo_2022}, \texttt{Seurat}\cite{hao_2021}, \texttt{Giotto}\cite{dries_2021} to name a few, and allow further theme customization with ease.

@@

\subsection*{Availability of data and materials}
The spatial transcriptomics dataset was obtained from \texttt{spatialLIBD} (\href{http://research.libd.org/spatialLIBD}{research.libd.org/spatialLIBD}). The UMAP example follows the `using\_schex' vignette in the \texttt{schex} package (\href{https://www.bioconductor.org/packages/schex}{bioconductor.org/packages/schex}). The code that generates these figures is deposited at \href{https://github.com/boyiguo1/Manuscript_escheR}{github.com/boyiguo1/Manuscript\_escheR} (\textit{v1.0}).

@@

\subsection*{Acknowledgements}
BG would like to acknowledge Nicholas J. Eagles, Kristen R. Maynard, Mina Ryten, Leon Di Stefano, and Lukas M. Weber (appearing in alphabetic order of last name) for their helpful comments, feedback and suggestions on \texttt{escheR} functionality. Nicholas J. Eagles and Kristen R. Maynard are employed by the Lieber Institute for Brain Development; Mina Ryten is employed by University College London; Leon Di Stefano and Lukas M. Weber are from the Johns Hopkins Bloomberg School of Public Health, Department of Biostatistics.

>>>>

\subsection*{Availability and implementation}
The open source R package \texttt{escheR} is freely available on Bioconductor (\href{https://bioconductor.org/packages/escheR}{bioconductor.org/packages/escheR}).
% and Zenodo (\fixme{add link}).

@@

Here, we provide an open-source package called \texttt{escheR} (named after the graphic artist M.C. Escher) in the R programming language \cite{R}, leading to a simplified interface to navigate the implementation of the multi-dimensional visualization in 2D space. By adapting \texttt{ggplot2} standard, \texttt{escheR} can be seamlessly integrated into many popular spatial resolved toolboxes, such as \texttt{SpatialLIBD }\cite{pardo_2022}, \texttt{Seurat} \cite{hao_2021}, \texttt{Giotto} \cite{dries_2021} to name a few, and allow further theme customization with ease.

@@

\subsection*{Availability of data and materials}
The spatial transcriptomics dataset was obtained from \texttt{spatialLIBD} (\href{http://research.libd.org/spatialLIBD}{research.libd.org/spatialLIBD}). The UMAP example follows the `using\_schex' vignette in the \texttt{schex} package (\href{https://www.bioconductor.org/packages/schex}{bioconductor.org/packages/schex}). The code that generates these figures is deposited at \href{https://github.com/boyiguo1/Manuscript_escheR}{github.com/boyiguo1/Manuscript\_escheR} (Zenodo DOI: \href{https://zenodo.org/record/7915970}{10.5281/zenodo.7915970}). The open source software package \texttt{escheR} available in the R programming language is freely available on GitHub (\href{https://github.com/boyiguo1/escheR}{github.com/boyiguo1/escheR}) and Bioconductor (\href{https://bioconductor.org/packages/escheR}{bioconductor.org/packages/escheR}).

@@

\subsection*{Acknowledgements}
We would like to acknowledge Nicholas J. Eagles, Kristen R. Maynard, Mina Ryten, Leon Di Stefano, and Lukas M. Weber (appearing in alphabetic order of last name) for their helpful comments, feedback and suggestions on \texttt{escheR} functionality. Nicholas J. Eagles and Kristen R. Maynard are employed by the Lieber Institute for Brain Development; Mina Ryten is employed by University College London; Leon Di Stefano and Lukas M. Weber are from the Johns Hopkins Bloomberg School of Public Health, Department of Biostatistics.
